---
title: Supplementary Materials for the paper 'a Review of R Neural Network Packages (with NNbenchmark)$:$
  Accuracy and Ease of Use'
author:
- Salsabila Mahdi^[Universitas Syiah Kuala, Indonesia]
- Akshaj Verma^[Manipal Institute of Technology, India]
- Christophe Dutang^[Université Paris-Dauphine, University PSL, France]
- Patrice Kiener^[InModelia, France]
- John C. Nash^[Telfer School of Management, University of Ottawa, Canada]
documentclass: article
classoption: a4paper
preamble: 
  includes: 
    \usepackage{float}
    \usepackage{multirow}
    \usepackage{subcaption}
    \usepackage{longtable}
    \newcommand{\code}{\texttt}
    \newcommand{\pkg}{\textbf}
    \newcommand{\soft}{\textsf}
geometry: "left=1cm,right=1cm,top=1cm,bottom=1.5cm"    
output:
  pdf_document: 
    toc: true
    number_sections: true
---

<!-- if we want html output, we may use https://rstudio.github.io/distill/ package -->


```{r, echo=FALSE}
library(knitr)
library(kableExtra)
library(NNbenchmark)
```



<!-- Table final result -->

```{r, echo=FALSE, message=FALSE}
options(knitr.kable.NA = '')

if(file.exists("./tables/Table1.csv")) {  
  Table1 <- read.table("./tables/Table1-final.csv", sep = ";", dec=".",
                       header=TRUE)
  Table1 <- Table1[Table1[,2] != "", ]
}else 
   Table1 <- rbind(rep("missing",6))

colnames(Table1) <- c("Package", "Algorithm", "Time", "RMSE",
                    "Util", "Doc", "Call")

pkg.name <- Table1$Package[Table1$Package != ""]
idx.pkg.name <- (1+0:NROW(Table1))[Table1$Package != ""]
Table1$Doc <- floor(Table1$Doc)

#repeat value
Table1$Package <- rep(pkg.name, times=diff(idx.pkg.name))
Table1$Util <- rep(Table1$Util[!is.na(Table1$Util)], times=diff(idx.pkg.name))
Table1$Doc <- rep(Table1$Doc[!is.na(Table1$Doc)], times=diff(idx.pkg.name))
Table1$Call <- rep(Table1$Call[!is.na(Table1$Call)], times=diff(idx.pkg.name))

#convert to stars
cvt2star <- function(j)
{
  switch(as.character(j), "0" = " ", "1"="*", "2"="**", "3"="***", "4"="****")
}
Table1$Doc <- unlist(sapply(Table1$Doc, cvt2star))
Table1$Util <- unlist(sapply(Table1$Util, cvt2star))
Table1$Call <- unlist(sapply(Table1$Call, cvt2star))

#reorder columns
Table1 <- Table1[, c(1, 5:7, 2:4)]
#get the min RMSE by pkg
pkgRkbyRMSE <- sort(tapply(Table1$RMSE, Table1$Package, min))
#create new index
n <- NROW(Table1)
getorderbypkg <- function(p)
{
  idx <- (1:n)[Table1$Package == p]
  if(length(idx) > 1)
    return(idx[order(Table1[idx, "RMSE"])])
  else
    return(idx)
}
idxRk <- unlist(sapply(names(pkgRkbyRMSE), getorderbypkg))
Table1rk <- Table1[idxRk, ]
rownames(Table1rk) <- 1:n

```

<!-- Table of discarded packages -->
```{r, echo=FALSE, message=FALSE}
options(knitr.kable.NA = '')

if(file.exists("./tables/Table2-UTF8-cleaned.csv")) {  
#  Table2 <- read.csv("./tables/Table2.csv", sep = ";", encoding="latin1")
  Table2 <- read.csv("./tables/Table2-UTF8-cleaned.csv")
  Table2 <- Table2[Table2[,3] != "", ]
  Table2 <- Table2[,c("Package", "Category", "Reason.to.Discard..Where.")]
}else
 Table2 <- rep("missing", 3)
colnames(Table2) <- c("Package", "Category", "Reason to Discard (File(s) and/or function(s))")


```


<!-- Additional Table for final result -->

```{r, echo=FALSE, message=FALSE}
options(knitr.kable.NA = '')

if(file.exists("./tables/Table3.csv")) {  
  Table3 <- read.csv("./tables/Table3.csv")
}else
 Table3 <- rep("missing", 7)
colnames(Table3) <- c("Package::algorithm", "RMSE min", "RMSE median", "RMSE D51", 
                      "MAE median", "WAE median", "Time median")

TOP5algo <- subset(Table1rk, RMSE %in% 1:5)[, c("Package", "Algorithm")]
rownames(TOP5algo)  <- subset(Table1rk, RMSE %in% 1:5)[, "Package"]

Table3$Package <- sapply(strsplit(Table3[, "Package::algorithm"], "::"), head, n=1)
Table3$Algorithm <- TOP5algo[Table3$Package, "Algorithm"]
idx2shorten <- grep("(BFGS)", Table3$Algorithm)
Table3$Algorithm[idx2shorten] <- substr(Table3$Algorithm[idx2shorten], 1, nchar(Table3$Algorithm[idx2shorten])-6)
Table3 <- Table3[, c("Package", "Algorithm", "RMSE min", "RMSE median", 
                     "RMSE D51", "MAE median", "WAE median", "Time median")]
Table3[, c("RMSE min", "RMSE median", "RMSE D51", "MAE median", "WAE median", "Time median")] <- apply(Table3[, c("RMSE min", "RMSE median", 
                     "RMSE D51", "MAE median", "WAE median", "Time median")],
      2, signif, digits=4)

```


<!-- Parameter Table -->

```{r, echo=FALSE, message=FALSE}
if(file.exists("./tables/TableAppendixC.csv")) {  
  Table1SupplApp <- read.csv("./tables/TableAppendixC.csv", sep = ";") 
}else 
  Table1SupplApp <- rep("missing",8)
colnames(Table1SupplApp) <- c("Num", "Input format", "Maxit", "Learn. rate", "median",
                    "d51", "MAE", "WAE")
#Table1SupplApp[, "Package:Algorithm"] <- paste0(Table1[Table1SupplApp$Num, "Package"], ":",
#                        substr(Table1[Table1SupplApp$Num, "Algorithm"], 4, nchar(Table1[Table1SupplApp$Num, "Algorithm"])))
#Table1SupplApp <- Table1SupplApp[, c("Num", "Package:Algorithm", "Input format", "Maxit", "Learn. rate", "median",
#                    "d51", "MAE", "WAE")]

Table1SupplApp[, "Package"] <- Table1[Table1SupplApp$Num, "Package"]
Table1SupplApp[, "Algorithm"] <- Table1[Table1SupplApp$Num, "Algorithm"]

Table1SupplApp <- Table1SupplApp[, c("Package","Algorithm", "Input format", "Maxit", "Learn. rate", "median",
                    "d51", "MAE", "WAE")]

#use idxRk as for Table1rk
if(all(Table1SupplApp[, "Algorithm"] == Table1$Algorithm))
{
  Table1SupplApp <- Table1SupplApp[idxRk, ]
  rownames(Table1SupplApp) <- 1:NROW(Table1SupplApp)
}

TOP5pkg <- head(unique(Table1rk$Package), 5)
TOP5algo <- head(Table1rk$Algorithm[order(Table1rk$RMSE)], 5)
TOP5algo <- substr(TOP5algo, 5, nchar(TOP5algo))
TOP5sentence <- paste0("TOP5 are ", paste(paste(TOP5pkg, TOP5algo, sep=":"), collapse=", "), ".")      

```

\newpage
# Additional materials on small/medium-size datasets for all packages 

```{r, echo=FALSE}
#custom format function
formatResultRable <- function(Table, orderRkRMSE)
{
  colnames(Table) <- c("Package::algorithm", "Time mean", "RMSE min", "RMSE median", "RMSE D51", 
                      "MAE median", "WAE median", "NPFA")

  Table$Package <- sapply(strsplit(Table[, "Package::algorithm"], "::"), head, n=1)
  
  Table$Algorithm <- sapply(strsplit(Table[, "Package::algorithm"], "::"), function(x) x[2])
  Table$Algorithm <- sapply(strsplit(Table$Algorithm, "_"), tail, n=1)
  Table$Algorithm <- gsub("none", "default", Table$Algorithm)
  Table$Algorithm <- paste0(Table$NPFA, ". ", Table$Algorithm)
  if(!missing(orderRkRMSE))
    Table <- Table[orderRkRMSE, c("Package", "Algorithm", "RMSE min", "RMSE median", "RMSE D51", 
                      "MAE median", "WAE median", "Time mean")]
  else
    Table <- Table[, c("Package", "Algorithm", "RMSE min", "RMSE median", "RMSE D51", 
                      "MAE median", "WAE median", "Time mean")]
  
  rownames(Table) <- 1:NROW(Table)
  Table
}

```


## Result for dataset `mDette`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/mDette-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for mDette") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak


## Result for dataset `mFriedman`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/mFriedman-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for mFriedman") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak


## Result for dataset `mIshigami`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/mIshigami-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for mIshigami") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak


## Result for dataset `mRef153`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/mIshigami-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for mRef153") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak


## Result for dataset `uDmod1`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/uDmod1-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for uDmod1") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak


## Result for dataset `uDmod2`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/uDmod2-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for uDmod2") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak


## Result for dataset `uDreyfus1`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/uDreyfus1-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for uDreyfus1") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak



## Result for dataset `uDreyfus2`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/uDreyfus2-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for uDreyfus2") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak



## Result for dataset `uGauss1`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/uGauss1-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for uGauss1") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak


## Result for dataset `uGauss2`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/uGauss2-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for uGauss2") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak


## Result for dataset `uGauss3`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/uGauss3-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for uGauss3") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak



## Result for dataset `uNeuroOne`

```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/uNeuroOne-result-summary.csv")
resPerDataSet <- formatResultRable(resPerDataSet, idxRk)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for uNeuroOne") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```

\pagebreak





## Score probabilities


\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img/scoreprobperpkgBnW.png}
        \label{fig:scoreprob}
        \caption{Score probabilities of \code{package:algorithm}}
\end{figure}

<!--## Appendix E-->

\pagebreak

# Additional materials on the large dataset `bWoodN1` for TOP-10 packages




## Summary statistics for non top-5 packages

The table provides the summary statistics of the best run of NN packages over two runs
on the large dataset `bWoodN1`.



```{r, echo=FALSE}
resPerDataSet <- read.csv("tables-extra/bWoodN1-results-summary-nontop5.csv")


resPerDataSet <- formatResultRable(resPerDataSet)
kableExtra::kable(resPerDataSet, format = "latex", booktabs = TRUE, 
                  centering = TRUE, align="llcccccc",
                  caption="Result for bWoodN1") %>%
  column_spec(c(1, 2), bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign ="middle") %>%
  kable_styling(font_size=8, latex_options =c("hold_position")) %>%
  footnote(general="Statistics over 10 runs; time in seconds.", footnote_as_chunk=TRUE)
```




<!--\pagebreak-->

## Graphics for top-5 packages

Figures below provides some insights where a package performs reasonably well 
with respect to one explanatory variable and where the fit misses the correct behavior of
an explanatory variable.
It displays the average response per rounded explanatory variable for the predicted, 
the empirical and the theoretical values.
That is, the empirical value and the predicted value for the $j$th explanatory 
variable are respectively computed at x-value $x$ as
$$
\bar y^{emp}_j(x) = \frac1{n_x}  \sum_{i=1}^n y_i 1_{r(x_{i,j}) = x},~
\bar y^{pred}_j(x) =  \frac1{n_x} \sum_{i=1}^n \hat y_i 1_{r(x_{i,j}) = x},~~
n_x=\sum_{i=1}^n 1_{r(x_{i,j}) = x},
$$
where $r()$ denotes the round function with two decimal places and $y_i, \hat y_i$ 
stand respectively for the $i$th observed response and the $i$th predicted response.
For instance, \pkg{MachineShop}, \pkg{nnet}, \pkg{nlsr} do not correctly capture the sinusoidal 
aspect of explanatory variable $x_5$ on the expected response, whereas \pkg{rminer}, \pkg{validann}
miss the increasing non-linear trend of explanatory variable $x_1$ on the expected response.


\begin{figure}
    \centering    
    \includegraphics[width=\textwidth]{img/MachineShop.png}
        \label{fig:MachineShop}
        \caption{Average predicted mean per explanatory variable for \code{MachineShop}}
\end{figure}


\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img/nnet.png}
        \label{fig:nnet}
        \caption{Average predicted mean per explanatory variable for \code{nnet}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img/rminer.png}
        \label{fig:rminer}
        \caption{Average predicted mean per explanatory variable for \code{rminer}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img/nlsr.png}
        \label{fig:nlsr}
        \caption{Average predicted mean per explanatory variable for \code{nlsr}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img/validann.png}
        \label{fig:validann}
        \caption{Average predicted mean per explanatory variable for \code{validann}}
\end{figure}



